Response to Reviewers $Rev^1$

### 2020-04-02 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

        \begin{question}
            \todo{*****}
            Feedback and memory: p. 11. If $NTIC > 0$ is sufficient and true information closure is not required, then feedfoward networks can be conscious according to ICT. Also, in that case, memory is not necessary, as the video camera would have $NTIC > 0$ as long as it records from a stable environment. In that case $I(Y_{t+1}, Y_t) > 0$ and $I(Y_{t+1}, Y_t|E_t)$ is small. This issue here is that having information about the next state does not imply that there is any causation, so if $Y_t$ is highly correlated with $E_t$ and $E_t$ causes $Y_{t+1}$ then NTIC is high. (Thus the IIT emphasis on causation).\\
            If somehow the fact that Y must be informationally closed wrt X does the heavy-lifting here that should be made more explicit (see above).
        \end{question}

@@

    			\item We agree with the reviewer's comment. 
    			In fact, in ICT, we do not differentiate states of processes between activation and relation. Take neural networks as an example, activation and structure states of a neural network should be both considered. After all, they are all just parameters of the process of the neural network. The only difference between the two groups of the parameters is the temporal scales of the parameter changes. States of activation may have more rapid dynamics than states of relation. In ICT, this is crucially related to the coarse-graining at the temporal domain which we did not address in this article but can be generalised in the future versions of ICT.

@@

    	\begin{ans}
    		\todo{What should we deal with this?}
    	\end{ans}

>>>>

        \begin{question}
            Feedback and memory: p. 11. If $NTIC > 0$ is sufficient and true information closure is not required, then feedfoward networks can be conscious according to ICT. Also, in that case, memory is not necessary, as the video camera would have $NTIC > 0$ as long as it records from a stable environment. In that case $I(Y_{t+1}, Y_t) > 0$ and $I(Y_{t+1}, Y_t|E_t)$ is small. This issue here is that having information about the next state does not imply that there is any causation, so if $Y_t$ is highly correlated with $E_t$ and $E_t$ causes $Y_{t+1}$ then NTIC is high. (Thus the IIT emphasis on causation).\\
            If somehow the fact that Y must be informationally closed wrt X does the heavy-lifting here that should be made more explicit (see above).
        \end{question}

@@

    			\item We agree with the reviewer's comment. 
                In fact, we do not differentiate states of processes between activation and relation. Take neural network as an example; the relations between elements are determined by the topology of a network (structure) and  its hyperparameters (e.g. activation functions). We agree that activation and relation of a neural network should be both considered. After all, they are all merely the parameters for the process of the neural network. The only difference between the two groups of the parameters is the temporal scales of changes. States of activation may have more rapid dynamics than states of relation. In ICT, the two sets of parameters do not have any qualitative differences.

@@

    	\begin{ans}
    		We have invited a native English speaker for proofreading. Please inform us if it is still not clear and readable. 
    	\end{ans}
